A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-05-11 paper/paper1/ms.tex
A few more sentences on the grazing exospheres

A few benefits of of this planet category arise.  First, they would expand the sample of planets for which the planetary winds could be measured, by relaxing the narrow geometrical transit probability of $1-10^\circ$ to something closer to $\pm30^\circ$, depending on the mass loss and gas dynamics.  In particular, the smallest stars such as white dwarfs and M-dwarfs could see the search space for exospheres increase by $10-100\times$.  Second, the range of viewing angles would serve as a natural experiment for constraining the vertical extent of outflows in the first place.  The typical bow shock 3D morphology could be deduced from a sample of otherwise-similar planets with a range of orbital inclinations.  Non-detections would therefore be valuable, especially in cases where $\sin{i}$ could be constrained independently.  In practice these additional constraints are rarely possible.  Finally, for some promising planet candidates a distinctive helium signal could validate the planet, assuming the signal could be disambiguated from stellar variability via velocity structure and phasing.

>>>>

A few benefits of of this planet category arise.  First, they would expand the sample of planets for which the planetary winds could be measured, by relaxing the narrow geometrical transit probability of $1-10^\circ$ to something closer to $\pm30^\circ$, depending on the mass loss and gas dynamics.  In particular, the smallest stars such as white dwarfs and M-dwarfs could see the search space for exospheres increase by $10-100\times$.  Second, the range of viewing angles would serve as a natural experiment for constraining the vertical extent of outflows in the first place.  The typical bow shock 3D morphology could be deduced from a sample of otherwise-similar planets with a range of orbital inclinations.  Non-detections would therefore be valuable, especially in cases where $\sin{i}$ could be constrained independently.  In practice these additional constraints are rarely possible, so ensemble statistical methods may have to be employed.  Finally, for some promising planet candidates a distinctive helium signal could validate the planet, assuming the signal could be disambiguated from stellar variability.  That disambiguation may be feasible, since the velocity structure and phasing of stellar and planetary Helium signals diverge due to stellar wind confinement and a launching from a predictable planetary rest frame.  The elusive category of young planets could be ideal, since their large radii and high intrinsic temperatures and high incident XUV radiation may yield large mass loss rates if they have recently migrated to an interior location through disk migration.  This category is especially valuable if discovered through near-IR RV searches, since abundant multi-epoch spectroscopy may already contain the requisite stellar variability baselines.
